# Insights! {#insights}

(Instructions for authoring a collection of course-related insights)

## Overview 
### Abstract:
In paralell with your other work, you will maintain an insights! page on which you collect valuable insights and learning experiences of the course. Through this you ask yourself: what does this material mean - for the field, and for myself.

### Objectives:

  * Self-reflect on the meaning of the course contents.
  * Question and develop your own attitudes about the course and the field.
  * Concisely record essential insights.

### Outcomes:

  * Through your continuos work on the insights! page you have ...
  * Developed an understanding of what makes a learning activity meaningful;
  * Identified and summarized the most meaningful learning experiencers in the course;
  * Authored a collection of insights that can remind you of the course experience.

### Deliverables:
  1. Your insights! page that is linked from your user page on the Student Wiki.

### Prerequisites:
This unit builds on material covered in the following prerequisite units:

  * [Journal Unit](#journal)
 
 
### Evaluation
Your insights! page will be evaluated by the instructor at the end of the course for a maximum of 5 marks. Find the evaluation rubric [here](http://steipe.biochemistry.utoronto.ca/abc/index.php/ABC-Rubrics#Insights).

## Insights
<pre>Big whirls have little whirls
that feed on their velocity,
and little whirls have lesser whirls
and so on to viscosity.
~[Lewis Fry Richardson](https://en.wikipedia.org/wiki/Lewis_Fry_Richardson) </pre>

It's rare that a fundamental insight is formulated so memorably, but it is so very valuable to step back and ask yourself: what was really important about what I just did? What is the one thing I should remember? Maintaining such a high-level perspective goes a long way to ensure that your learning effort turns into something valuable. Begin an insights! page that collects your most important ideas about this term. Be concise and succinct - focus on the essence of your experience. And if you can put it into rhyme - all the more memorable.

  * Consider the marking [rubric](http://steipe.biochemistry.utoronto.ca/abc/index.php/ABC-Rubrics#insights.21): continuous engagement is important, as well as successfully grasping the essence of what you are doing. You are welcome to study other's pages, and to quote, but you must give credit where appropriate. Be very careful not to plagiarize.

`r task_counter <- task_counter + 1`
## Task `r task_counter`

```{block2, type="rmd-task"}
  * Make a link to a new insights! page as a subpage of your user page on the Student Wiki.        
  * Make sure the page is created in the correct namespace, not in the main space of the Wiki.
    * Edit the page to give it a meaningful structure.
    * Add a category tag [[Category:Insights!]] to the page.
    * As with all course-material, add a {{CC-BY}} tag to the bottom of the page to include a Creative Commons license.
    * Whenever you make an interesting observation about the course, the material, or something else that you find inspiring, add it to your page.
    * You can write only your insight, but it may be more valuable to add a bit of context. You may certainly review and revise, strenghten or discard insights throughout the term. And you are encouraged to study others opinions. However: be mindful that your insights are your own, personal, unique reflections. I could imagine one or two such insights per week.
```

    
## Template
You can use the following template of Wikitext for your insights or design your own. Take care: formatting counts for evaluation.:

```{r eval=FALSE}
====<Insight Title>====
 
<context... >
;<insight>
:<date>
 
{{Vspace}}

```


## Further reading, links and resources
 
**If in doubt, ask!**<br>
If anything about this learning unit is not clear to you, do not proceed blindly but ask for clarification. Post your question on the course mailing list: others are likely to have similar problems. Or send an email to your instructor.

```{block2, type="rmd-original-history"}
<br>**Author**: Boris Steipe <boris.steipe@utoronto.ca> <br>
**Created**: 2017-08-05<br>
**Modified**: 2017-08-07<br>
Version: 1.0<br>
**Version history**:<br>
1.0 Live version<br>
0.1 First stub<br>
 
``` 

### Updated Revision history
```{r echo=FALSE}
source("./bcb420_books_helper_functions.R")
if (git2r::in_repository(".")) {
  knitr::kable(githistory2table(git2r::commits(repo = ".", path = knitr::current_input())))
} else {
  cat("No Git history available.")
}

```

