# Netiquette - (Network Etiquette)

(Etiquette for the Internet and for this course)

## Overview 
### Abstract:
Netiquette is a portmanteau of "network etiquette". It is a collection of social conventions for communication on the Internet such as e-mail, mailing lists, forums ... Here is a subset of relevance for our courses and workshops.

### Objectives:
Read about the basic rules and courtesies for communicating effectively and professionally in mailing lists and internet forums.

### Outcomes:
Apply the principles discussed on the page consistently throughout the course.
Identify weaknesses and propose updates.

### Deliverables:
**Time management**: Before you begin, estimate how long it will take you to complete this unit. Then, record in your course journal: the number of hours you estimated, the number of hours you worked on the unit, and the amount of time that passed between start and completion of this unit.

**Journal**: Document your progress in your Course Journal. Some tasks may ask you to include specific items in your journal. Don't overlook these.

**Insights**: If you find something particularly noteworthy about this unit, make a note in your insights! page.

  * Is there a pet-peeve of yours that is not mentioned here? Initiate a discussion on that on the course mailing list or contribute to the discussion if one has already started.
  * Is this page still up to date? Cultural norms change, and our communication habits have changed tremendously in the past decade. Propose updates and/or improvements on on the course mailing list or contribute to the discussion if one has already started.

---
 
## Be kind

This is the single most important rule. We are all working together. Let's all make this a pleasant and exciting experience.
 
 
## Pay attention who you reply to

If you use "reply", your message will go the entire list. Pause a moment, and consider whether this is what you want. Perhaps your message is of interest to only a single recipient? Or your message may be personal, or confidential ...
 
 
## Use informative subject lines

Spend a moment thinking what your post is about, then condense the message into a few words. This goes a long way towards:

  * allowing the recipients to estimate how interested they are in the contents of your message;
  * retrieving a thread in your archived messages;
  * browsing the archives for information;
  * keeping the ensuing discussion on topic.
  * Try to be specific for example, 
    * this subject line is poor: Chimera doesn't work!
    * Much better would be: Can't load molecule in Chimera after editing coordinates
  * If you must change the subject line, quote the old line as in: New subject (was: old subject)

## Don't hijack threads

If you have a new question, never simply write it into the reply to an older thread. This is called "Thread Hijacking" and it is rude and ineffective and it will cause me to have a poor opinion of your manners. If you hijack a thread:

  * your new question will end up in an unrelated discussion;
  * it will be much harder to search;
  * the original poster's question gets diluted and may never get appropriately discussed;
  * you demonstrate that you didn't actually care enough to type up a subject line.
  * Use your mail-client's reply function if you contribute to a thread, write a new mail or post if you have something new to add. ^[Some mailing list software builds thread based on subject line and some software builds thread based on message ID. Only changing the subject line may not be sufficient to start a new thread. Since you usually don't know which does what, use the rule above to be sure.]
  * As a corollary: if your post is related to the thread, by all means do use the reply function of your mail client and don't change the subject line, even if you think the original subject line was not well written or contained a (non-critical) typo etc.
 
 
## Follow the discussion

From time to time I see questions asked that have already been answered previously. This shows me that you did not follow the discussion. What do you think I think of that?
Exactly.
 
## Describe problems clearly

Sometimes your problems will be due to a faulty assumption, sometimes due to incompatible software, sometimes due to bugs, or errors in assigned tasks ... The more clearly you describe what you did and what happened, the more likely it is someone will be able to help. Simply stating "this or that didn't work" will get you nowhere. Ask yourself:

  1. Did I specify the circumstances under which the problem arose?
  1. Did I specify exactly what happened and what I believe the problem is?
  1. Have I given enough information so that someone else would be able to reproduce the problem?
 
 
## Avoid screenshots

Almost always when I see a screenshot of errors that arise during assignments, the issue would have been better described by copy/pasting code and text. Screenshots, as images, are a dead-ends for further analysis.

  * If you paste a screenshot with a sequence ID, others will need to type it out, awkwardly, on a different page to reproduce your problem.
  * If you paste a screenshot with a piece of code, others will have to type the code, awkwardly, into their code editor to reproduce your problem and experiment for a solution.
  * If you paste a screenshot of an error message, it is that much more work to Google for the message and figure out what could have caused it.

In all those cases, you prevent others from helping you quickly and effectively and you are wrong to expect others to type down the contents of your images because you didn't copy/paste the essential material. That's not smart. Also you are wasting other's bandwidth on their computers or mobile devices. That's rude.

The only case where screenshots are encouraged is where an image is involved - but even then, for example when discussing R plots, the code that has generated the plot would be more helpful. dput() is your friend. And learn to create MWEs (Minimal Working Examples).
 
 
## Show us that you've done your homework
The ["How to Ask Questions the Smart Way"](http://www.catb.org/~esr/faqs/smart-questions.html) document gives the following excellent advice:

<pre>
Hasty-sounding questions get hasty answers, or none at all. The more you do to demonstrate having put thought and effort into solving your problem before seeking help, the more likely you are to actually get help. [...]

Never assume you are entitled to an answer. [...]

You will earn an answer, if you earn it, by asking a substantial, interesting, and thought-provoking question - one that implicitly contributes to the experience of the community rather than merely passively demanding knowledge from others.
</pre>

I can't put it any better.
 
 
## Use mixed case and write full words

Using UPPERCASE ONLY IS THE TYPOGRAPHIC EQUIVALENT OF SHOUTING; this is appropriate only under exceptional circumstances. some people use lowercase only. are they too lazy to find the caps key?

```{r eval=FALSE}
It also looks lik u cant B rly botherd 2 rite 
if u rite ur txt with textN shorth&.
``` 
 
## Don't Troll
<font size="15" color="red">Just don't do it, oK?</font>
 
**Also remember: trolling, stalking, impersonating etc. may fall under sanctionable offences of the [University's Student Code of Conduct](https://governingcouncil.utoronto.ca/secretariat/policies/code-student-conduct-february-14-2002).**
 
 
## No need to directly address someone

Sending a message to the list reaches all list members. That's the point of the list: we are sharing discussions with everyone. There is no need to address anyone in particular (not even your professor), unless you are responding publicly to a specific statement by that person. Even generic salutations - like Howdy or Dear all, are nowadays usually omitted for the sake of brevity.
 
 
## Resolve when done
Once the problem has been solved, there is no need to thank contributors - but don't just walk away, you are not done! It is very important to share feedback whether the advice received has worked or not, or if something else worked instead. People helping you on a mailing list don't expect a reward except for one thing: the little satisfaction that their effort was actually helpful. Don't deny that, that would be rude.

A separate reason to resolving such threads is that they are archived, and when others are looking for their solution they need to be able to tell whether there is hope to be found here.
 
 
## Self-evaluation
**Question 1**: Zachary has run into an issue when downloading an R package. He posts a screenshot of his computer in the mailing list to ask what could have gone wrong. Good or bad? ^[**Bad**.Reread the "Avoid screenshots" section above if you disagree.]
 
**Question 2**:Amadeus has been following a discussion on the mailing list about Zachary's problem. That reminds him that he wasn't sure how to find a package that contains a particular function. He replies to Zachary's thread and asks his question. Good or bad? ^[**Bad**. Reread the "Don't hijack threads" section above if you disagree.]
 
**Question 3**:Kaila responds to a post I have made, about some subtleties in identifying homologous sequences by sequence alignment. She is in a hurry and doesn't address me by name in her post. Good or bad? ^[**Good**. Reread the "No need to directly address someone" section above if you disagree.]

## Further reading, links and resources

  * Dall'Olio et al. (2011) Ten simple rules for getting help from online scientific communities. PLoS Comput Biol 7:e1002202. (pmid: 21980280)<br>
[PubMed](https://www.ncbi.nlm.nih.gov/pubmed/?term=21980280)
  * [Netiquette - Virginia Shea's Core Rules of Netiquette](http://www.opentextbooks.org.hk/ditatopic/4851)
  * [How to create a Minimal, Complete, and Verifiable example – R advice via stackoverflow.](https://stackoverflow.com/help/minimal-reproducible-example)
  * [How to Ask Questions the Smart Way for the technical minded, excellent advice!](http://www.catb.org/~esr/faqs/smart-questions.html)
 
**If in doubt, ask!**<br>
If anything about this learning unit is not clear to you, do not proceed blindly but ask for clarification. Post your question on the course mailing list: others are likely to have similar problems. Or send an email to your instructor.

 
```{block2, type="rmd-original-history"}
<br>**Author**: Boris Steipe <boris.steipe@utoronto.ca> <br>
**Created**: 2017-08-05<br>
**Modified**: 2017-08-17<br>
Version: 1.1<br>
**Version history**:<br>
1.1 Add thread resolution (Gabi Morgenshterns suggestion).<br>
1.0 First live version using contents from an old page.<br>
0.1 First stub<br>
 
```

### Updated Revision history
```{r echo=FALSE}
source("./bcb420_books_helper_functions.R")
if (git2r::in_repository(".")) {
  knitr::kable(githistory2table(git2r::commits(repo = ".", path = knitr::current_input())))
} else {
  cat("No Git history available.")
}

```

### Footnotes: 
